Analysing the effect of land-use type on the proportion of scouts

### 2022-02-08 analysis/landuse_effect_prop_scouts.Rmd
increased size of loading plot labels

loading_plot <- ggplot(
  data = argi.rural.loadings,
  aes(
    x = Landuse, y = Correlation
  )
) +
  geom_boxplot(aes(fill = Landuse), lwd=0.1) +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = rural_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5)
  ) +
  annotate(
    "rect",
    ymin = -cutoff,
    ymax = cutoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text()
  ) +
  scale_fill_manual(
    values = c(
      "Arable" = "#CCBB44", "Built Up Area" = "#EE6677",
      "Non Agricultural Unmanaged Green Space" = "#228833",
      "Water" = "#4477AA", Other = "#BBBBBB"
    )
  )

@@

loading_plot <- ggplot(
  data = urban.loadings,
  aes(
    x = Landuse, y = Correlation
  ),
  fill = Landuse
) +
  geom_boxplot(aes(fill = Landuse), lwd=0.1) +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = urban_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5)
  ) +
  annotate(
    "rect",
    ymin = -cutoff,
    ymax = cutoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text()
  ) +
  scale_fill_manual(
    values = c(
      "Continuous Central" = "#BBBBBB", "Dense Residential" = "#BBBBBB",
      "Sparse Residential" = "#EE6677", "Railway" = "#CCBB44",
      "Parks Allotments Cemeteries" = "#228833",
      "Water" = "#BBBBBB", Other = "#BBBBBB"
    )
  )

>>>>

loading_plot <- ggplot(
  data = argi.rural.loadings,
  aes(
    x = Landuse, y = Correlation
  )
) +
  geom_boxplot(aes(fill = Landuse), lwd=0.1) +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = rural_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5), size = rel(textsize)
  ) +
  annotate(
    "rect",
    ymin = -cutoff,
    ymax = cutoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text()
  ) +
  scale_fill_manual(
    values = c(
      "Arable" = "#CCBB44", "Built Up Area" = "#EE6677",
      "Non Agricultural Unmanaged Green Space" = "#228833",
      "Water" = "#4477AA", Other = "#BBBBBB"
    )
  )

@@

loading_plot <- ggplot(
  data = urban.loadings,
  aes(
    x = Landuse, y = Correlation
  ),
  fill = Landuse
) +
  geom_boxplot(aes(fill = Landuse), lwd=0.1) +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = urban_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5), size = rel(textsize)
  ) +
  annotate(
    "rect",
    ymin = -cutoff,
    ymax = cutoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text()
  ) +
  scale_fill_manual(
    values = c(
      "Continuous Central" = "#BBBBBB", "Dense Residential" = "#BBBBBB",
      "Sparse Residential" = "#EE6677", "Railway" = "#CCBB44",
      "Parks Allotments Cemeteries" = "#228833",
      "Water" = "#BBBBBB", Other = "#BBBBBB"
    )
  )
